Thesis: draft

### 2021-05-21 draft.tex
Update draft.tex
changed Ch.2 SBM

The construction of the model is similar to that of the regular stochastic block model. For a SBM-WS with $n_c$ communities of specified sizes, we first construct $n_c$ Watts-Strogatz networks (for each constituent Watts-Strogatz network the rewire probability $\beta$ and the mean degree $\left<k\right>$ are specified), then edges are (with some predefined probability) randomly added between the different Watts-Strogatz communities. The result is a network that can be tuned to have both a community structure and a high clustering coefficient. This is different from the regular stochastic block model that can only account for a community structure and lacks high clustering.
% talk about community sizes from power law??

@@

The previous two chapters, Chapter \ref{chap2} and \ref{chap3}, gave a broad overview of networks and opinion dynamics models respectively. In this chapter we will summarize the specific networks and opinion dynamics models that are used in this thesis. \\
\newline
Section \ref{networkmodel} gives an overview of the network models that are used. In chapter \ref{chap2}, Section \ref{netModel} we discussed their main properties; here we will discuss why we use these networks. Which of their properties are of interest in this thesis? What are their benefits and possible shortcomings regarding to our goals?\\
\newline
In section \ref{realnetwork}, we will discuss the used real-world networks. The reasons of choosing these specific networks will be explained, together with their possible strengths and weaknesses.\\ % + explain where they come from?
\newline
Finally, Section \ref{opinionmodel} summarizes and discusses the opinion dynamics model that is implemented. We will focus on possible advantages and disadvantages of the model.

\section{Network models}\label{networkmodel}

\textbf{The stochastic block model}\\
\newline
One of the main features of the stochastic block model is the ability to generate networks with community structure. We will therefore use this model to investigate the impact of community structure on the evolution of opinions and the formation of echo chambers.\\
\newline
It is expected that community structure will enhance the formation of echo chambers compared to the random network case. The question remains, however, whether the influence of community structure on the formation of echo chambers is of the same caliber as that of high clustering. It is also of interest to study the possible relation between the appearance of echo chambers and the modularity of the network.\\
\newline
The stochastic Watts-Strogatz block model is used as a model that has both high clustering and community structure. We will check if the combination of both features displays any difference in the formation of echo chambers compared to having only a single feature (either community structure or high clustering).

@@

ADD THIS IN AS LIMITATIONS/FUTURE DIRECTIONS (about activation probabilities)

>>>>

The construction of the model is similar to that of the regular stochastic block model. For a SBM-WS with $n_c$ communities of specified sizes, we first construct $n_c$ Watts-Strogatz networks (for each constituent Watts-Strogatz network the rewire probability $\beta$ and the mean degree $\left<k\right>$ are specified), then edges are (with some predefined probability) randomly added between the different Watts-Strogatz communities. The result is a network that can be tuned to have both a community structure and a high clustering coefficient. This is different from the regular stochastic block model that can only account for a community structure and lacks high clustering.\\
\textbf{The stochastic block model in this thesis}\\
The stochastic block model is used to generate networks with community structure. We will therefore use this model to investigate the impact of community structure on the evolution of opinions and the formation of echo chambers.\\
It is expected that community structure will enhance the formation of echo chambers compared to the random network case. The question remains, however, whether the influence of community structure on the formation of echo chambers is of the same caliber as that of high clustering. It is also of interest to study the possible relation between the appearance of echo chambers and the modularity of the network.\\
The stochastic Watts-Strogatz block model is used as a model that has both high clustering and community structure. We will check if the combination of both features displays any difference in the formation of echo chambers compared to having only a single feature (either community structure or high clustering).

@@

@@

ADD THIS IN AS LIMITATIONS/FUTURE DIRECTIONS (about activation probabilities) + PAY ATTENTION TO FEEDBACK (see file)
